\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-08 paper.tex
Modify theory. Incorporate new figures.

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}L:#1}}
\title{\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results } }

\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

The structural behavior of nanostructured materials  has  become a
topic  of global  interest,  where numerous  research has been
done so far \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PSi the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN optical elements from PSi
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

@@

\section{Theory}
\subsection{Electrostatic Model for Photonic Crystals with Gradient
  Refraction Index (EMPCGRIN)}

The calculate  current density in a GRIN structure produced by an
electrochemical attack on Si to produce Porous Si with a
position-dependent porosity due to the distance to the counter
electrode. A simplifies  calculation  with geometry,
assumimg  in the form of a whole prism on the sides a, b, c with a, b
horizontal and c vertical. Here c considered as the height of the
liquid, and the walls are insulating, but the bottom is completely
covered with the sample, which act as good conductor. The electrode is
a thin insulated cable with tip, which  a point  current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical. I'll take as the height of the liquid. The walls are insulating, but the bottom is completely covered by the sample, I suppose it is a good conductor. The tip of the electrode is a thin insulated wire located at $ \vec{r}_0 $.}}
\end{figure}
The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $
\sigma $ is the conductivity. This for the stationary case $
\bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived
from the electric potential, $\vec {E} = - \bigtriangledown \varphi
$.
And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the
sample is a relatively good conductor, when connected to earth $
\varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere
superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
The current density that carries the current to the tip. So
\begin{equation}
  \int ds \cdot \vec{E} = \dfrac{I}{\sigma}
\end{equation}
The problem to be solved is thus, to obtain the potential produced by a point charge,
\begin{equation}
  q_{_{0}} = \dfrac{I}{4 \pi \sigma}
\end{equation}
In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the
tip of the electrode that is in the presence of a ground conductor
plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0,
y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of
the liquid is also not conductive to $ (x, y, c) $, the normal current
is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E}
\cdot \hat{n}=0  $. i.e
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b ,z)=E_{{_z}}(x, y ,c)=0
\end{equation}
This has a mixture of Dirichlet-Neumann type boundary conditions. By
using the simplified prism geometry  can solve the problem using the
theory of image loads. Each load has an image of the same sign and
magnitude for each lateral insulating surface and the opposite sign
change in the lower part of the conductive plane, as follows.
 \begin{figure}
 \centering
 \includegraphics[scale=.6]{Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
     real charge in the corner of the cell with its charges ($ q $)
     images of the same sign in $ Z_0 $ and another charge image ($ -q
     $) with change of sign located below the conductor in position $
     -Z_0 $. b) The upper face seen from above, a real load and its
     image loads in $ Z_0 $. c) All this formed a systems of a real
     load and its image loads produced by the cell walls and its other
     images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

@@

Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle

@@

calculate the complex refractive index $ \tilde{n}_{_{PSi}} = n_{_
  {PSi}} - ik_{_{PSi}} $ of a porous layer with homogeneous porosity

@@

coefficients at the interfaces $aire/PSi$ y $PSi/c-Si$ which are

@@

 p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{air}}+\varepsilon_{_{PSi}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{Si}}+
   \varepsilon_{_{PSi}}}

@@

 where $ p $ is the volume fraction of air within the PSi layer

@@

 $\varepsilon_{_{PSi}}$ represents the dielectric function of PSi. The

@@

 \subsection{Fabrication  of Microcavities of Porous Silicon GRIN }
 A conventional way to fabricate the porous silicon microcavity (MC)
 is a defect with a mode located between two DBRs (Distributed Bragg
 Reflector). Alternate layers of high refractive index (H) and low (L)
 refractive index are obtained, satisfying the Bragg condition
 $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $. The
 defect must meet the condition
 $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the
 following sequence: $$ (HL)_6 HH (LH )_6 $$
 Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu
 m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $,
 $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$,
 $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $. All of this data is for
 the $ 0 $ point of the sample that is located at one end of the
 sample just below the tip counter-electrode.\\
 Our proposal for the fabrication of porous silicon GRIN microcavities
 uses the same conditions for fabrications of porous silicon GRIN
 monolayers as in section 3.1, and taking the conventional data
 mentioned above. The porous silicon microcavities (PSiMC) with
 gradient refractive index (GRIN), were manufactured with different
 current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a
 current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim
 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $. Also
 for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for
 low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the
 corresponding  porosities of $ 0.75 $ to $ 0.64 $. Using our
 calibration ratio to design GRIN structures,  the corresponding
 current density for each measurement point.

\section{Discussion and Results}
\subsection{Simulation of the EMPCGRIN model}
 To test the developed  idea in the theoretical section, we find a
 relation of the tip of the counter electrode that acts similarly as a
 point charge and the current density for a geometry in an
 electrolytic box and solve the electrostatic equations with suitable
 boundary conditions. Resulting in an electrostatic model for photonic
 crystals with a refractive index with gradient (EMPCGRIN).
\begin{figure}
  \centering
  \includegraphics[scale=0.7]{Images/G123}
  \caption{\emph{ Simulation to calculate the current density in
      a structure with gradient refractive index (GRIN) produced
      by electrochemical attack on crystalline silicon to
      produce porous silicon (PSi), with a current density
      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
      cm $} Eq. (\ref{Eq:J})}.
  \label{fig:DR1}
\end{figure}
We consider Fig. \ref{fig:DR1} which come from solving
Eq. (\ref{Eq:J}), calculating the current density as a function of the
rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
PERL PDL package and corresponding graph in gnuplot. We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect. We use as length $a =
2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
evaluated at the surface on the silicon interface, in the plane $ Z =
0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
profile $ J (mA / cm^2) $ normalized with the electric current $ I
(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
sample, a change of contrate due to the different densities of
attacked currents. We see the decay behavior that the profile has as
Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
vary the currents we can observe the behavior of changes in the
normalized current density, with the data obtained through the
simulation we could have a better optimization in the design of porous
silicon proposing a new and novel experimental arrangement, in the
same way we can give ourselves an idea by means of the graph of how
the attack would be and the formal side of the pores in the silicon.

@@

 cm) $ and $ C (1.7 \ \ cm) $, from the sample of PSi GRIN $ G1 (I = 5

@@

 SEM. The formation of PSi GRIN in the thickness occurs due to the

@@

  \caption{\emph{Characterization of a monolayer of PSi GRIN G1

@@

density. Therefore, if it is desired to manufacture a PSi monolayer of

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

\notaL{No entiendo nada de la introducción}
The structural properties of nanostructured materials  has  received a
considerable attention,  and a large research effort has been devoted
to them \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PS) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PS the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN optical elements from PS
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

@@

\section{Theory}
\subsection{Calculation of the current density}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the speed of attack and the width of the
porous layer. Nevertheless, it is not a simple to task to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures. Thus, a system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be in principle be numerically calculated for a
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a good conductor which is
electrically grounded. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{¿Está bien la polaridad de la batería?}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = \frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

The effective conductivity of the relatively thin sample in contact
with the grounded counterelectrode is large enough that we may assume its
surface $z=0$ is an equipotential.
On the other hand, no current can go across the insulating walls of
the cell, situated at $x=0$, $x=a$,, $y=0$ and $y=b$, nor through the
free surface of the liquid at $z=c$. Thus, the problem to solve is Poisson
equation with a point charge source
\begin{equation}
  \label{eq:poisson}
  \nabla^2\varphi=-4\pi q_0\delta(\bm r-\bm r_0),
\end{equation}
with mixed boundary conditions
\begin{equation}
  \label{eq:ground}
  \varphi(x,y,0)=0,
\end{equation}
and
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b
,z)=E_{{_z}}(x, y ,c)=0.
\end{equation}
This problem may be solved readily using image charge theory
\notaL{ref}. The potential within the electrolytic cell coincides the
the field within an infinite vacuum containing the point charge
$q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
charges. The images include a reflection on the conducting bottom of the
cell, of the opposite charge $-q_0$ and situated at $(x_0, y_0,-z_0)$,
to guarantee that the bottom stays at potential zero.
There are further images on the four walls of the cell, of the same charge $q_0$
and situated at $(-x_0,Y_0,z_0)$, $(x_0,-y_0, z_0)$, $(2a-x_0, y_0,
z_0)$ and $(x_0, 2b-y_0,z_0)$ to guarantee that no current goes across
them. Similarly, there is an image of the same charge $q_0$ at
$(x_0,y_0,2c-z_0)$ to guarantee that no current goes across the
surface of the electrolyte. Furthermore, each image charge has to be
further reflected by each of the aforementioned surfaces, yielding new
images.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{paper-1}
  \caption{Top view of the electrolytic cell (light blue) showing the charge at the
    tip of the electrode (red dot) and its images on the walls of the
    rectangular cell, the images of its images and so on (blue dots). The walls are at $x=0,a$,
    $y=0,b$. The relation of some charges and their images is
    indicated by dashed arrows, with a bar to indicate the
    corresponding reflecting wall. The system may be interpreted as a
    periodic lattice with a rectangular unit cell of size $2a\times 2b$,
    one of which is indicated  by wide dashed lines, and with a basis of four equal
    charges at $(\pm x_0, \pm y_0, z_0)$.}
  \label{fig:topview}
\end{figure}
In Fig. \ref{fig:topview} we illustrate the real charge and all of
its images within the plane $z=z_0$. They form a periodic rectangular
lattice with a unit cell of size $2a\times 2b$ and with a basis of
four equal charges situated at the positions $\bm r_0$, $\bm
r_1=(-x_0, y_0, z_0)$, $\bm r_2=(x_0, -y_0, z_0)$ and $\bm r_3=(-x_0,
-y_0, z_0)$. In Fig. \ref{fig:sideview} we show a lateral view of the
image charges.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{paper-2}
  \caption{Side view of the electrolytic cell (light blue)
    showing the charge at the tip of the electrode (red dot), its
    images within the plane $z=z_0$ (blue dots), and its images at the
    surface of the sample and the top of the electrolyte (green
    dots). We use solid dots to denote particles with the same charge
    as that corresponding to the tip $q_0$, and open dots for those of
    opposite charge. The system may be interpreted as a periodic
    lattice with a rectangular unit cell of size $2a\times 4c$, one of
    which is indicated by wide dashed lines, and with a basis of four
    charges $q_0$ and another four charges $-q_0$.}
  \label{fig:sideview}
\end{figure}

This has a mixture of Dirichlet-Neumann type boundary conditions. By
using the simplified prism geometry  can solve the problem using the
theory of image loads. Each load has an image of the same sign and
magnitude for each lateral insulating surface and the opposite sign
change in the lower part of the conductive plane, as follows.
 \begin{figure}
 \centering
 \includegraphics[scale=.6]{Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
     real charge in the corner of the cell with its charges ($ q $)
     images of the same sign in $ Z_0 $ and another charge image ($ -q
     $) with change of sign located below the conductor in position $
     -Z_0 $. b) The upper face seen from above, a real load and its
     image loads in $ Z_0 $. c) All this formed a systems of a real
     load and its image loads produced by the cell walls and its other
     images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

@@

Poisson equation $ \nabla^2 \phi = -4 \pi \displaystyle

@@

calculate the complex refractive index $ \tilde{n}_{_{PS}} = n_{_
  {PS}} - ik_{_{PS}} $ of a porous layer with homogeneous porosity

@@

coefficients at the interfaces $aire/PS$ y $PS/c-Si$ which are

@@

 p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PS}}}{\varepsilon_{_{air}}+\varepsilon_{_{PS}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PS}}}{\varepsilon_{_{Si}}+
   \varepsilon_{_{PS}}}

@@

 where $ p $ is the volume fraction of air within the PS layer

@@

 $\varepsilon_{_{PS}}$ represents the dielectric function of PS. The

@@

 \subsection{Fabrication  of Microcavities of Porous Silicon GRIN }
 A conventional way to fabricate the porous silicon microcavity (MC)
 is a defect with a mode located between two DBRs (Distributed Bragg
 Reflector). Alternate layers of high refractive index (H) and low (L)
 refractive index are obtained, satisfying the Bragg condition
 $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $. The
 defect must meet the condition
 $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the
 following sequence: $$ (HL)_6 HH (LH )_6 $$
 Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu
 m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $,
 $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$,
 $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $. All of this data is for
 the $ 0 $ point of the sample that is located at one end of the
 sample just below the tip counter-electrode.\\
 Our proposal for the fabrication of porous silicon GRIN microcavities
 uses the same conditions for fabrications of porous silicon GRIN
 monolayers as in section 3.1, and taking the conventional data
 mentioned above. The porous silicon microcavities (PSMC) with
 gradient refractive index (GRIN), were manufactured with different
 current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a
 current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim
 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $. Also
 for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for
 low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the
 corresponding  porosities of $ 0.75 $ to $ 0.64 $. Using our
 calibration ratio to design GRIN structures,  the corresponding
 current density for each measurement point.

\section{Discussion and Results}
\subsection{Simulation of the EMPCGRIN model}
 To test the developed  idea in the theoretical section, we find a
 relation of the tip of the counter electrode that acts similarly as a
 point charge and the current density for a geometry in an
 electrolytic box and solve the electrostatic equations with suitable
 boundary conditions. Resulting in an electrostatic model for photonic
 crystals with a refractive index with gradient (EMPCGRIN).
\begin{figure}
  \centering
  \includegraphics[scale=0.7]{Images/G123}
  \caption{\emph{ Simulation to calculate the current density in
      a structure with gradient refractive index (GRIN) produced
      by electrochemical attack on crystalline silicon to
      produce porous silicon (PS), with a current density
      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
      cm $} Eq. (\ref{Eq:J})}.
  \label{fig:DR1}
\end{figure}
We consider Fig. \ref{fig:DR1} which come from solving
Eq. (\ref{Eq:J}), calculating the current density as a function of the
rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
PERL PDL package and corresponding graph in gnuplot. We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect. We use as length $a =
2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
evaluated at the surface on the silicon interface, in the plane $ Z =
0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
profile $ J (mA / cm^2) $ normalized with the electric current $ I
(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
sample, a change of contrate due to the different densities of
attacked currents. We see the decay behavior that the profile has as
Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
vary the currents we can observe the behavior of changes in the
normalized current density, with the data obtained through the
simulation we could have a better optimization in the design of porous
silicon proposing a new and novel experimental arrangement, in the
same way we can give ourselves an idea by means of the graph of how
the attack would be and the formal side of the pores in the silicon.

@@

 cm) $ and $ C (1.7 \ \ cm) $, from the sample of PS GRIN $ G1 (I = 5

@@

 SEM. The formation of PS GRIN in the thickness occurs due to the

@@

  \caption{\emph{Characterization of a monolayer of PS GRIN G1

@@

density. Therefore, if it is desired to manufacture a PS monolayer of
